\documentclass[10pt,a4paper]{article}

% Required Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fontawesome5} % For icons

% Page Layout
\geometry{
    a4paper,
    left=1.2cm,
    right=1.2cm,
    top=1.0cm,
    bottom=1.0cm
}

% Colors
\definecolor{primary}{RGB}{0, 70, 140}
\definecolor{text}{RGB}{40, 40, 40}
\definecolor{lighttext}{RGB}{100, 100, 100}

% Hyperlink configuration
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    filecolor=primary,      
    urlcolor=primary,
}

% Section formatting
\titleformat{\section}
  {\Large\bfseries\color{primary}} % Format
  {} % Label
  {0em} % Sep
  {} % Before code
  [\vspace{-0.5em}\rule{\textwidth}{0.5pt}] % After code

\titlespacing*{\section}{0pt}{1ex plus 1ex minus .2ex}{0.5ex plus .2ex}

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{4pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

% -------------------------------------------------------------------------
% -------------------------------------------------------------------------

\begin{document}

\color{text}

% Heading
\begin{center}
    {\Huge \textbf{MOHAMED AMER}} \\ \vspace{2pt}
    {\large Data Scientist \& Machine Learning Engineer} \\ \vspace{2pt}
    \small 
    \faIcon{envelope} \href{mailto:mohamed_amer_01@protonmail.com}{mohamed\_amer\_01@protonmail.com} ~|~
    \faIcon{phone} +46 793016889 ~|~
    \faIcon{map-marker-alt} Halmstad, Sweden ~|~
    \faIcon{linkedin} \href{https://www.linkedin.com/in/mohamed-amer-5a7a55255}{LinkedIn} ~|~
    \faIcon{github} \href{https://github.com/ham0di01}{GitHub}
\end{center}

% ----------- Professional Summary -----------
\section{Professional Summary}
\vspace{2pt}
\small{Data Scientist and Machine Learning Engineer with hands-on experience developing predictive models and optimizing complex processes at Volvo SML. Proficient in Python, TensorFlow, and PyTorch, with a strong background in leveraging AI to solve real-world logistical and industrial challenges. Dedicated to building efficient, scalable solutions that drive measurable business value.}
\vspace{2pt}

% ----------- Education -----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Halmstad University}{Halmstad, Sweden}
      {M.Sc. Artificial Intelligence}{Expected June 2026}
    \resumeSubheading
      {Halmstad University}{Halmstad, Sweden}
      {B.Sc. Computer Science}{June 2023}
  \resumeSubHeadingListEnd

% ----------- Work Experience -----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Student Researcher}{Nov. 2024 -- June 2025}
      {Volvo SML}{Gothenburg, Sweden}
      \resumeItemListStart
        \resumeItem{Integrated into the on-site logistics team at Volvo SML to analyze and streamline complex supply chain processes.}
        \resumeItem{Developed and evaluated predictive machine learning models to optimize logistics flows across large-scale datasets.}
        \resumeItem{Collaborated directly with field engineers to translate data-driven insights into deployable efficiency improvements.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

% ----------- Thesis Projects -----------
\section{Research Publications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://urn.kb.se/resolve?urn=urn:nbn:se:hh:diva-57027}{\textbf{Prediction Intervals for ML-driven Logistics}} $|$ \emph{Master's Thesis at Volvo SML}}{Nov. 2024 -- June 2025}
          \resumeItemListStart
            \resumeItem{Developed demand forecasting models with prediction intervals to improve inventory management.}
            \resumeItem{Implemented discrete-event simulation and Beta-PERT distributions, reducing costs while maintaining high service levels.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://urn.kb.se/resolve?urn=urn:nbn:se:hh:diva-51061}{\textbf{Room Booking and Access Control System}} $|$ \emph{Bachelor's Thesis at Halmstad University}}{Jan. 2023 -- June 2023}
          \resumeItemListStart
            \resumeItem{Built an integrated system for room bookings and access control using NodeJS, Android Studio, and PostgreSQL.}
            \resumeItem{Implemented secure Mobile BankID authentication and developed mobile apps to resolve booking conflicts and unauthorized access.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

% ----------- Side Projects -----------
\section{Side Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/ham0di01/chest-xray-classification}{\textbf{Chest X-Ray Classification}}}{}
          \resumeItemListStart
            \resumeItem{Developed a CNN model using TensorFlow for medical image analysis.}
            \resumeItem{Achieved 92\% validation accuracy.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/ham0di01/mlops-forecasting-service}{\textbf{Spare-Parts Demand Forecasting}}}{}
          \resumeItemListStart
            \resumeItem{Built a complete MLOps pipeline using Prophet, LightGBM, and FastAPI.}
            \resumeItem{Implemented end-to-end machine learning workflow for demand prediction.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/ham0di01/pattern-finder}{\textbf{Pattern Finder – Trading Patterns with Computer Vision}}}{}
          \resumeItemListStart
            \resumeItem{Developed a system using computer vision to identify technical patterns in trading charts.}
            \resumeItem{Implemented matching against historical crypto data to find similar price scenarios.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

% ----------- Technical Skills -----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript, C, SQL, MATLAB} \\
     \textbf{Machine Learning \& Data}{: TensorFlow, PyTorch, Scikit-learn, Pandas, NumPy} \\
     \textbf{Generative AI \& LLMs}{: RAG, Prompt Engineering, Claude Code, GenAI Architectures} \\
     \textbf{MLOps \& Infrastructure}{: CI/CD, Docker, Git, REST APIs, Cloud Platforms} \\
     \textbf{Core Concepts}{: Advanced OOP, Data Structures \& Algorithms, Statistical Modeling}
    }}
 \end{itemize}

% ----------- Languages -----------
\section{Languages \& References}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Languages}{: Swedish (Native), English (Advanced C1), Arabic (Native)} \\
     \textbf{References}{: Available upon request.}
    }}
 \end{itemize}

\end{document}
